\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{geometry}
\usepackage{parskip}
\input{glyphtounicode}

% Adjust margins
\geometry{
  top=0.75in,
  bottom=0.75in,
  left=0.75in,
  right=0.75in
}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Add space between paragraphs
\setlength{\parskip}{6pt}

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

\begin{document}

September 3, 2024

Boston Scientific \\
Hiring Manager \\
Arden Hills, MN 55112

Dear Hiring Manager,

I am writing to express my strong interest in the Manufacturing Tech II - 1st Shift position at Boston Scientific in Arden Hills, MN. With my background in electrical engineering and embedded firmware, I believe I would be a valuable asset to your team and contribute significantly to Boston Scientific's mission of advancing science for life.

As an Embedded Firmware Engineer at Bobcat Company, I successfully implemented and validated the transition from CAN to automotive ethernet in vehicles, increasing data transmission speeds from 500 kbps to 100 Mbps. This experience aligns perfectly with the role's requirement to work with engineers in set-up, calibration tasks, and system debugging on electronic test equipment. Additionally, I engineered a secure method for remote vehicle updates, reducing the likelihood of future field campaigns by 25%.

My experience as a Teaching Assistant at the University of Minnesota Duluth has honed my skills in providing one-on-one debugging assistance and implementing process improvements. These skills will be invaluable in identifying and troubleshooting process, material, or equipment problems to minimize downtime in the manufacturing environment.

Furthermore, my internship at NASA Glenn Research Center involved implementing critical components using VHDL and conducting over 100 simulations to validate performance under various conditions. This experience has prepared me well for the challenges of evaluating operating data and conducting on-line adjustments to products, instruments, or equipment.

Key qualifications that make me a strong fit for this role include:
\begin{itemize}
    \item Strong technical background with a BS in Electrical Engineering (Computer Engineering), graduating with a 3.95 GPA
    \item Proven record of working closely with engineers on complex projects
    \item Experience in reading electrical schematics and part drawings
    \item Understanding of medical device documentation requirements
    \item Strong software aptitude, including proficiency in Python, C/C++, VHDL, and various frameworks and tools
    \item Experience with preventative maintenance, calibration tasks, and system debugging on electronic equipment
\end{itemize}

I am particularly drawn to Boston Scientific's commitment to solving challenges that matter most in medical science. Your focus on transforming lives through innovative medical solutions aligns perfectly with my career aspirations. I am confident that my technical expertise, problem-solving abilities, and strong desire to learn new skills would make me a valuable addition to your Manufacturing Tech team.

Thank you for considering my application. I look forward to the opportunity to discuss how I can contribute to Boston Scientific's mission. I am available at your convenience for an interview and can be reached via the contact information provided on my resume.

Sincerely,

Kennedy Mindeman

\end{document}